---
title: "Mapping harassment in Yelahanka"

description: "A citizen centric tool to report harassment and assault inside Yelahanka. Visualise our community's citizen reported crime data on a map."
draft: false

####################### Banner #########################
banner:
  title : "Documenting harassment in Yelahanka"
  content : "_**A citizen centric tool to report harassment and assault inside Yelahanka. Visualise our community's citizen reported crime data on a map.**_ \n \n ಯಲಹಂಕದ  ನಗರವಾಸಿಗಳಿಗೆ  ಇಲ್ಲಿ ನಡೆಯುವ ದೌರ್ಜನ್ಯ ಮತ್ತು ಕಿರುಕುಳವನ್ನು ರಿಪೋರ್ಟ್ ಮಾಡುವ ಉಪಕರಣ. ಇಲ್ಲಿ ಸಂಗ್ರಹವಾದ ಅಪರಾಧ ವರದಿಗಳನ್ನು ನಕ್ಷೆಯ ಮೇಲೆ ಕಾಣಬಹುದು "
  button:
    enable : true
    label : "Report / ಘಟನೆಯನ್ನು ರಿಪೋರ್ಟ್ ಮಾಡಿ"
    link : "report" 
 
##################### Feature #######################
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE) 

library(tidyverse) 
library(dplyr)

library(sf)
library(leaflet)
library(leaflet.providers) 
library(leaflet.extras)

library(htmltools)
library(crosstalk)

library(lubridate)
library(DT)
library(widgetframe)
```

```{r reading data, include=FALSE}
#imports data from multiple spreadsheets and performs operations to uniformize field names
oldData <- read_csv('../resources/assets/allUshahidiResponses.csv') 
newData <- read_csv('../resources/assets/latestReports.csv') 

# post verification
#if human verified is 'yes'
newData <- newData %>% filter(`human verified`== 'yes')

#if published on Ushahidi (safeyelli.ushahidi.io)
oldData <- oldData %>% filter(`Post Status` == 'published')


#match field names in the old sheet to new
oldData <-oldData %>% rename( description = `Describe the incident in detail`,
                   `kind of incident` = `What kind of incident was this?`,
                   `date and time` = `When and at what time this happen?`,
                   `gender of victim` = `What is your gender?`,
                   `environmental factors` = `What was wrong with the space?` 
                   )

#combine data and time in the new sheet
newData$`time of incident` <- paste(format(as.POSIXct(newData$`time of incident`), format = "%H:%M"))
                                    

# Force IST time to UTC time for storage and operations. 
# UTC is recommended, all time must be stored as UTC, need to modify google sheets?
# lubridate as_datetime returns nothing here
newData$`date and time` <- paste(newData$`date of incident`, newData$`time of incident`) %>% 
  as.POSIXct() %>%  force_tzs(tzones = "Asia/Kolkata", tzone_out = "UTC")


#split the location field into lat and lng
newData <- newData %>% separate( col = `location`, into = c("Location.lat", "Location.lon"), sep = "\\,") 

#old data coords into chr for compatibility
newData <- newData %>% 
  mutate(Location.lat = as.double(Location.lat),
         Location.lon = as.double(Location.lon))

# map tiles from mapbox
mapUrl="https://api.mapbox.com/styles/v1/rungdung/cku6gh76r1dvh17o3zkfllvjz/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoicnVuZ2R1bmciLCJhIjoiY2tqeWh6cXF4MDgzMjJvbWVmbGQzYjAwMyJ9.U-aJyoqyKvTXlhVk43jV1A"
```



```{r merging dataframes and creating sf frames, include=FALSE}
# combine dataframes for leaflet 
allData <- bind_rows(oldData, newData)
allData <- rename(allData, lat=Location.lat, lng = Location.lon)

# Attach a coordinate reference 
allData <- allData %>%
  st_as_sf(coords = c('lng', 'lat'),crs = 4326) 
```

```{r operations on data, echo=FALSE, message=FALSE, warning=FALSE}
# create unique date and time fields to simplify leaflet
allData <- allData %>% 
  mutate(date = as.Date(`date and time`, '%d/%m/%Y'),
         year = as.character(year(date)),
         month = as.character(month(date)),
         hour = as.integer(format(as_datetime(allData$`date and time`, tz="Asia/Kolkata"), 
                           format="%H"))
         )
```

```{r Formatting popup text, message=FALSE, warning=FALSE, include=FALSE}
# create popup text for the leaflet map, all formatting is done in html
allData$popupText <- 
  paste0('<strong>', allData$`kind of incident`, '</strong> <br/> <br/>',
         format(
           as_datetime(allData$`date and time`, tz="Asia/Kolkata"),
           format='%B %d %Y, Time: %H %M'
           ),
         '<br/> <br/>', 
         allData$`description`, ' ') %>% 
  lapply(htmltools::HTML)
```

```{r Creating shared data frame for crosstalk, echo=FALSE, message=FALSE, warning=FALSE}
# sharedData is the format for crosstalk. Crosstalk enables filters by sharing dataframes on a static site.
sharedD <- SharedData$new(allData)
```

```{r Mappinnng!, echo=FALSE, message=FALSE, warning=FALSE}

#leaflet object
#addProviderTiles(providers$CartoDB.Positron) not working
map <- leaflet(sharedD) %>%
  addTiles(urlTemplate = mapUrl) %>%
  fitBounds(77.564292, 13.096725, 77.591393, 13.109996) %>%
  setMaxBounds(77.554808, 13.087922, 77.608495, 13.114213) %>%
  addScaleBar() %>%
  addLayersControl(
    #baseGroups = c("Incidents"),
    overlayGroups = c("Heat Map", "Incidents"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  
   addMarkers(
    popup = paste(allData$popupText),
    popupOptions = popupOptions(maxWidth = 400),
    #clusterOptions = clusterOptions(),
    group = "Incidents",
  ) %>%

  
  addHeatmap(
    radius = 20,
    blur = 20,
    intensity = 0.7,
    cellSize = 0.1,
    minOpacity = 0.4,
    max = 0.9,
    group = "Heat Map"
  )

# OSM data overlay on map
# Layers
# addPolygons(data = emptyPlot,
#             color = 'grey',
#             stroke=FALSE,
#             label = emptyPlot$Name,
#             group="Empty Plots") %>%
# addPolygons(data = infrasPlot,
#             color = 'red',
#             stroke=FALSE,
#             label = infrasPlot$Name,
#             group="Dilipated infrastructure") %>%
# addPolygons(data = shopPlot,
#             color = 'green',
#             stroke=FALSE,
#             label = shopPlot$Name,
#             group="Shops")
```

```{r formatting output,echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}

# filters
#dateFilter <- filter_slider("date", "", sharedD, column= ~date, step=3, width=800)
typeFilter <- filter_checkbox("Incident type", "Type", sharedD, group= ~`kind of incident`, inline = FALSE )
yearFilter <- filter_checkbox("Year", "Year", sharedD, group= ~year, inline = FALSE )
timeOfDayFilter <- filter_slider("Hour","Time of Day (24H format)", sharedD,  column=~hour, step=1, width=200, min=0, max=24)



# map display
tags$div(class = "map-section",
           #dateFilter,
           tags$div(class = "crosstalk-map",
                    map),
           tags$div(class = "crosstalk-filters", tags$h4('Map filters:'), yearFilter, typeFilter, timeOfDayFilter),
           #tags$div(class = "crosstalk-map",
                    #displayData),
                    
         )

#widgetframe::frameWidget(displayData)
```


`r blogdown::shortcode_open("faq", "Why should you report?")`
> "Because it's on you to always do the right thing"

If you are being harassed, there are certain steps you can take to stop them. If you don't report it, they're just going to keep doing it. You now have the power to do something about it. Every report helps us paint a more comprehensive picture, essentially mapping these crimes in order to influence policing and public policy. 
`r blogdown::shortcode_close("faq")`

`r blogdown::shortcode_open("faq", "How can you help?")`
> **"If you see something, do something"**

If you see sexual assault, harassment or catcalling happen to someone else or if something happens to you, go to the police and file a report. Additionally, take 5 minutes and fill out this form so that you can contribute to a larger cause with your story.
`r blogdown::shortcode_close("faq")`

`r blogdown::shortcode_open("faq", "Why does it matter?")`
> **"Because If you don't do anything about it, you become complicit"**

As socially responsible human beings, it is our duty to do everything we can to make sure that the world is a safer place today than it was yesterday. Seems far fetched? Well, Let's start with making our immediate surroundings safe. Let's strive towards a society where a woman can walk down the street without fear of harassment! 
`r blogdown::shortcode_close("faq")`

# Defining harassment and other terms
 
(The law provides a clear enough definition of assault)

1.  Assault: Whoever assaults or uses criminal force to any woman(or man\*), intending to outrage or knowing it to be likely that he will thereby outrage her modesty (Sec 354 IPC).

2.  Harassment:  Sexual harassment is unwanted behaviour of a sexual nature which: violates your dignity. makes you feel intimidated, degraded or humiliated. creates a hostile or offensive environment.

Section 506 IPC - criminal intimidation. (Reverse the gender roles and it still constitutes harassment. Women can also be reported under 506 - Criminal intimidation)\

Even though there is no 'catcalling' or 'eve teasing' law in India. People often use Sec 294 IPC in cases relating to such offences

3.  Obscene acts and songs.---Whoever, to the annoyance of others---
 
    (a) does any obscene act in any public place, or

    (b) sings, recites or utters any obscene song, ballad or words, in or near any public place 
    

