---
title: "Mapping harassment in Yelahanka"
subtitle: "A citizen centric tool to report harassment and assault inside Yelahanka. Visualise your community's citizen reported crime data on a map."
description: "A citizen centric tool to report harassment and assault inside Yelahanka. Visualise your community's citizen reported crime data on a map."
draft: false
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) 
library(sf)
library(leaflet)
library(leaflet.providers)
library(leaflet.extras)
library(rgdal)
library(htmltools)
```

```{r reading data, include=FALSE}
oldHarassData <- read_csv('../resources/assets/formResponses2.csv') 
#oldHarassData <- oldHarassData %>% separate(., col = `What are the exact coordinates of the incident?`, into = c("Location.lat", "Location.lon"), sep = "\\,")

newHarassData <-read_csv('../resources/assets/ushahidiResponses2.csv')

mapUrl="https://api.mapbox.com/styles/v1/rungdung/cku6gh76r1dvh17o3zkfllvjz/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1IjoicnVuZ2R1bmciLCJhIjoiY2tqeWh6cXF4MDgzMjJvbWVmbGQzYjAwMyJ9.U-aJyoqyKvTXlhVk43jV1A"
```



```{r merging dataframes and creating sf frames, include=FALSE}
allData <- rbind(oldHarassData,newHarassData)
allData <- rename(allData, lat=Location.lat, lng = Location.lon)

# Attach a coordinate reference 
allCoords <- allData %>%
  st_as_sf(coords = c('lng', 'lat'),crs = 4326)
```


```{r Mappinnng!, echo=FALSE, out.width='100%'}
#addProviderTiles(providers$CartoDB.Positron) not working
map <- leaflet(allCoords) %>%
  addTiles(urlTemplate = mapUrl) %>%
  fitBounds(77.554808, 13.087922, 77.608495, 13.114213) %>%
  setMaxBounds(77.554808, 13.087922, 77.608495, 13.114213) %>%
  
  addScaleBar() %>%
  addLayersControl(
    baseGroups = c("Heat Map", "Incident markers"),
    #overlayGroups = c("Empty Plots", "Dilipated infrastructure", "Shops"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  
  addMarkers(
    #label = allCoords$`Describe the incident in detail`,
    #labelOptions = labelOptions(textsize = "10px", width),
    popup = htmlEscape(allCoords$`Describe the incident in detail`),
    popupOptions = popupOptions(maxWidth = 400),
    #opacity=0.09,
    #fillColor = ~pal(`Year of Occurence`),
    clusterOptions = markerClusterOptions(),
    group = "Incident markers"
  ) %>%
  
  addHeatmap(
    radius = 20,
    blur = 20,
    intensity = 0.7,
    cellSize = 0.1,
    minOpacity = 0.4,
    max = 0.9,
    group = "Heat Map"  
  )
# Layers
# addPolygons(data = emptyPlot,
#             color = 'grey',
#             stroke=FALSE,
#             label = emptyPlot$Name,
#             group="Empty Plots") %>%
# addPolygons(data = infrasPlot,
#             color = 'red',
#             stroke=FALSE,
#             label = infrasPlot$Name,
#             group="Dilipated infrastructure") %>%
# addPolygons(data = shopPlot,
#             color = 'green',
#             stroke=FALSE,
#             label = shopPlot$Name,
#             group="Shops")
map
```


# Defining harassment and other terms 

(The law provides a clear enough definition of assault) 

1.  Assault: Whoever assaults or uses criminal force to any woman(or man\*), intending to outrage or knowing it to be likely that he will thereby outrage her modesty (Sec 354 IPC).

2.  Harassment:  Sexual harassment is unwanted behaviour of a sexual nature which: violates your dignity. makes you feel intimidated, degraded or humiliated. creates a hostile or offensive environment.

Section 506 IPC - criminal intimidation. (Reverse the gender roles and it still constitutes harassment. Women can also be reported under 506 - Criminal intimidation)\

Even though there is no 'catcalling' or 'eve teasing' law in India. People often use Sec 294 IPC in cases relating to such offences

3.  Obscene acts and songs.---Whoever, to the annoyance of others---
 
    (a) does any obscene act in any public place, or

    (b) sings, recites or utters any obscene song, ballad or words, in or near any public place \

 
# Report an incident 

If you would to have your incident listed on this map, you can reach out to us to record your story. The map will be updated periodically.
 
<a href="report" class="btn btn-primary">Report an Incident</a>

</iframe>
